\newglossaryentry{hmi}
{
    name={HMI},
    description={Human-Machine Interface is a system that allows humans to interact
    with a machine or computer system,
    often through a graphical user interface or touch screen.
    The HMI enables the user to control and monitor the machine or system,
    and provides feedback to the user about its status and performance}
    first={human-machine interface (HMI)},
    text={HMI}
}

\newglossaryentry{ccu}
{
    name={CCU}, 
    description={A component of a system that is responsible for coordinating
    and managing the activities of other components.
    In a computer system, the central control unit (CCU) is often
    the main processor or microcontroller that executes instructions
    and manages input/output operations.}
    first={central control unit (CCU)},
    text={CCU}
}

\newglossaryentry{sensor-card}
{
    name={Sensor card},
    description={A printed circuit board (PCB) or electronic module
    that contains one or more sensors,
    such as temperature sensors, humidity sensors,
    pressure sensors, or motion sensors.
    Sensor cards are often used in electronic systems for data acquisition,
    monitoring, or control purposes.},
    plural={sensor cards},
    first={sensor card},
    text={sensor card}
}

\newglossaryentry{rio}
{
    name={RIO},
    description={A type of input/output (I/O) system that is located away from the central processing unit (CPU) or main controller, and is connected through a network or communication link. Remote input/output (RIO) systems typically consist of one or more I/O modules that are connected to a communication interface or network adapter.},
    first={remote input/output (RIO)},
    text={RIO}
}

\newglossaryentry{actuator}
{
    name={Actuator},
    description={Device or mechanism that convert energy into physical motion or force, often used to control or manipulate a system. Examples of actuators include electric motors, solenoids, hydraulic cylinders, and pneumatic actuators. Actuators are commonly used in a wide range of applications, such as robotics, automation, and control systems.},
    plural={actuators},
    text={actuator}
}

\newglossaryentry{sbc}
{
    name={Single-board computer},
    description={A complete computer system built on a single circuit board, which includes all the basic components of a computer, such as a central processing unit (CPU), memory, input/output (I/O) ports, and storage. SBCs are designed to be compact, low-power, and cost-effective, and are often used for embedded systems, prototyping, and hobbyist projects. They can be used for a wide range of applications, such as robotics, Internet of Things (IoT) devices, and home automation. Examples of popular SBCs include the Raspberry Pi, BeagleBone, and Arduino.}
}

\newglossaryentry{imu}{
    name={IMU},
    description={A device that consists of multiple sensors, such as accelerometers, gyroscopes, and magnetometers, that measures the orientation, velocity, and gravitational forces of an object in motion. IMUs are commonly used in robotics, unmanned vehicles, and virtual reality systems to provide accurate position and motion tracking. They can also be used for stabilization and navigation purposes in aerospace and marine applications.},
    first={Inertial Measurement Unit (IMU)},
    text={IMU},
}

\newglossaryentry{medicolbox}
{
    name={MediColBox},
    description={The medicine colletion part of Medretur's solution for collecting
    the medicine},
    plural={MediColBoxes},
    first={MediColBox},
    text={MediColBox}
}

\newglossaryentry{intrusion}
{
    name={Intrusion},
    description={The act of intruding or the state of being intruded. especially: the act of wrongfully entering upon, seizing,
    or taking possession of the property of another},
    plural={intrusions},
    first={intrusion},
    text={intrusion}
}

\newglossaryentry{exploit}
{
    name={Exploit},
    description={An act of utilizing something to gain a benefit or advantage. The term can be used in various contexts, such as in technology, economics, or social interactions.},
    text={exploit}
}

\newglossaryentry{usb}{
    name={USB},
    description={Universal Serial Bus is a common interface that allows communication between computers and peripheral devices. It provides a standardized connection and protocol for connecting devices such as keyboards, mice, printers, and storage devices.}
}

\newglossaryentry{dsi}{
    name={DSI},
    description={Display Serial Interface is a specification used for connecting display panels to electronic devices. It provides a high-speed, serial communication interface for transmitting display data, control signals, and power between devices such as microcontrollers or graphics processing units and display panels.}
}

